% resume.tex
%
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

\documentclass[letterpaper,10pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black     % can put red here to visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.30}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} %\\
		%#5
\end{tabular*}\vspace{-6pt}}

\newcommand{\projectheading}[1]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1}
\end{tabular*}\vspace{6pt}}

\newcommand{\workheading}[3]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{#3} \\
		\textit{#2}
\end{tabular*}\vspace{6pt}}

%End Custom commands
%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{\href{https://github.com/rishidewan33}{\LARGE Rishi Dewan}} & \href{mailto:rishidewan33@gmail.com}{rishidewan33@gmail.com}\\
	{2704 Rio Grande St.\#512} & \href{https://github.com/rishidewan33}{https://github.com/rishidewan33} \\
	{Austin, TX 78705} & {Phone: 281-732-6108}\\
	\end{tabular*}
\\
\vspace{0.1in}

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
	\begin{itemize}
		\item
			\ressubheading{\href{http://www.utexas.edu}{The University of Texas at Austin}}{Austin, TX}{\href{http://www.cs.utexas.edu}{Bachelor of Science in Computer Science}}{Aug. 2006 -- May. 2011}%{GPA: 2.60/4.00}
				{
				\begin{itemize}
					\resitem{\textbf{Relevant Courses}: \href{http://www.cs.utexas.edu/users/mckinley/352/}{Computer Systems Architecture}, \href{http://www.cs.utexas.edu/~dahlin/Classes/UGOS/index.html}{Introduction to Operating Systems}, \href{http://www.cs.utexas.edu/~plaxton/c/357/index.html}{Design and Analysis of Algorithms}, \href{http://www.cs.utexas.edu/~novak/cs315.html}{Algorithms and Data Structures}}
				\end{itemize}
				}
	\end{itemize} % End Education list

\resheading{Technical Skills}
	\begin{description}
		\item[Language Experience:] {C/C++ (1 year), Java (4 years), Python (2 years)}
		\item[Programming Exposure in:] {C\#.NET, ASP.NET, UML, \LaTeX, HTML, CSS, SQL}
		\item[Computer and OS:] {Proficient in Ubuntu Linux, Windows 9x, XP, Vista, Mac OS X Snow Leopard}
		\item[Software:]{\href{http://msdn.microsoft.com/en-us/library/ms950416.aspx}{MS Visual Studio}, \href{http://netbeans.org/}{Netbeans IDE}, \href{http://git-scm.com/}{git}, \href{http://www.realvnc.com/}{RealVNC}, \href{http://www.openoffice.org/}{OpenOffice (and Microsoft Office)}, SSH Secure Shell, \href{http://www.gnu.org/software/gdb/}{GNU Debugger},VirtualBox}
		\item[Programming Paradigms:]{Object-Oriented Programming, Multithreaded Programming, Design Patterns}
	\end{description} % End Skills list

\resheading{Programming Projects}
	\begin{itemize}
		\item 
			\projectheading{Atomic Disk}
				{
				\begin{itemize}
					{Implemented an abstraction of a hard disk in Java which incorporated}
					{the use of transactions in order to apply reads/writes to multiple}
					{disk sectors in the disk abstraction atomically (i.e. as a single operation).}
				\end{itemize}
				}
		\item
			\projectheading{Cooperative Thread Package API}
				{
				\begin{itemize}
					{Developed a User-Level-Threads library in C which uses context manipulation}
					{to allow users to use the library to create and organize control of threads at a user level.}
				\end{itemize}
        			}
\begin{comment}
        	\item
			\projectheading{Proportional-Share Network Scheduler}
				{
				\begin{itemize}
					{Wrote methods for a network scheduler program in C++. Although}
					{not many lines of code were written, the goal of the project was to acquire}
					{experience in writing and debugging multithreaded code, as well as}
					{learning to correctly use synchronization data types such as monitors.}
				\end{itemize}
				}
\end{comment}
		\item 
			\projectheading{Advanced Encryption Standard Algorithm}
				{
				\begin{itemize}
					{Wrote an implementation of the AES algorithm, which is a symmetric-key encryption}
					{standard in both Java (128/256-bit) and Python (128/192/256-bit).}
				\end{itemize}
				}
\begin{comment}
		\item			
			\projectheading{L1 Cache Simulator}
				{
				\begin{itemize}
					{Programmed a Level 1 cache simulator in Java. This project was designed to give an understanding on how}
					{caching hardware work with respect to memory. The cache simulator's funtionally represents the functions}
					{of actual cache hardware, such as write backs, write allocations, and the LRU replacement algorithm.}
				\end{itemize}
				}
\end{comment}
		\item
			\projectheading{SET Puzzle Game}
				{
				\begin{itemize}
					{Implemented a GUI Python clone application of the puzzle card game SET \href{http://www.setgame.com}{(www.setgame.com)}.}
					{This program was an introduction into GUI Programming using Python's GUI toolkit}
					{\textit{TKinter}.}
				\end{itemize}
				}
	\end{itemize}  % End Experience list

\resheading{Work Experience}
	\begin{itemize}
	 \item
	    \workheading{University Unions}{Building Manager}{Sept. 2010 - May 2011}
	      { \begin{itemize}
	        \item{In charge of managing the security of all patrons in the building and the building itself.}
	        \item{Performed hourly rounds and performed cash escorts for employees within the building}
		\item{Learned to operate Mac OS X on the work computer by working with bash shell commands, and learning about various Mac applications}
	        \end{itemize}
	      }

	 \item
	    \workheading{University of Texas at Austin - Division of Housing and Food}{Night Supervisor}{Jan. 2009 - Mar. 2010}
	      { \begin{itemize}
	         \item{In charge of managing the safety and security of multiple thousands of residents located in the university dorms.}
		 \item{Resolved general problems (i.e. between resident advisors, dorm coordinators, and personnel in the housing department.)}
	        \end{itemize}
	      }
	\end{itemize} %End Work Experience List

% \resheading{Activities}
% \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
%   \item
%   {
%    {Assocation of Computing Machinery} & \textit{2008 - 2011}
%   }
%    {Indian Student Assocation} & \textit{2008 - 2010}
% \end{tabular*}



\vfill
\begin{flushright}
\em{This r\'{e}sum\'{e} was written and compiled in \LaTeX.}
\end{flushright}

% \resheading{General Skills}
% 	\begin{itemize}
% 	\item
% 	  \projectheading{Teamwork Oriented}
% 	    \begin{itemize}
% 	    \item{Worked with partners on program assignments, where we navigate through coding and point out and discuss potential errors and as well as design plans.}
% 	    \end{itemize}
% 	\item
% 	  \projectheading{Communication Skills}
% 	    \begin{itemize}
% 	     \item{Demonstrated while working on programming projects by communicating design and debugging ideas with project parnters. Also demonstrated }
% 	    \end{itemize}
% 	\item
% 	  \projectheading{Problem Solving Skills}
% 	    \begin{itemize}
% 	     \item{Given the programming projects that required strong understanding of the specifications, scrutinized designing and planning was executed in order to complete these projects.}
% 	    \end{itemize}
% 	\item
% 	  \projectheading{Strong Dedication}
% 	    \begin{itemize}
% 	     \item{Allocated many hours per week working on programming projects.}
% 	    \end{itemize}
% 	\item
% 	  \projectheading{TBD}
% 	    \begin{itemize}
% 	     \item{TBD}
% 	    \end{itemize}
% 	\end{itemize}

\end{document}